Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-03 thesis/experiment.tex
More write up work, redid the physical setup diagram

\subsection{Personal Computer}

Four computer systems were employed each with the same specifications.

@@

\cite{:qf}

@@

@@

All systems will be configured and connected to the same isolated network
through the hub as shown in Figure \ref{physical-setup}.

\begin{figure}[H]
  \centering\includegraphics[scale=0.6]{physical-setup}
  \caption{Physical Setup}
  \label{physical-setup}
\end{figure}

@@

Software is installed and configured on all machines. The simulation network is
configured to use the private Tor directory server rather than the public ones
specified by default \parencite{website:private-tor-network}.

The packet sniffer is configured to capture only the packets relevant for each
data set.

@@

\section{Systems}

A number of systems will be configured both physical and virtual. The \emph{Host Systems}, those running natively on a physical PC with a Virtual Box environment to host a Guest Operating System. The \emph{Guest Systems}, operating systems running inside a Virtual Box environment on top of a Host System, and the Sniffing system, which is responsible for capturing the experiment results.

The name, IP Address and role of each system in the simulation network is shown in Table \ref{table:hosts}.

\begin{tabular}{lrr}
  \toprule
  Host Name & IP Address & Role\\
  \midrule
  Grumman & 192.168.0.100 & Management and Host of Client System \\
  Arrakis & 192.168.0.001 & Host of Server System \\
  Richese & 192.168.0.102 & Host of Tor Network System \\
  \midrule
  Ipyr & 192.168.0.200 & Sniffing System \\
  \midrule
  Lankiveil & 192.168.0.16 & Client Guest System \\
  Ginaz & 192.168.0.17 & Server Guest System \\
  Sikun & 192.168.0.18 & Tor Network Guest System \\
  \botomrule
  \label{table:hosts}
\end{tabular}

@@

The sniffing system has a very basic role: to capture packets. It is configured with the Ubuntu 10.04 Server Operating system. Most basic features are disabled and tcpdump is configured to run at startup saving all captures to 1mb files in a directory indicating when the system was booted.

@@

\begin{itemize*}
  \item Install Ubuntu 10.04 Desktop Operating System
    \begin{itemize*}
      \item Use entire disk
      \item Set time zone to GMT +8 WST (Perth)
    \end{itemize*}
  \item Turn off automatic package updates
  \item Turn off powersaving features
  \item Install OpenSSH Server
  \item Add Virtual Box repository to sources.lst
  \item Update sources and install Virtual Box
  \item Ensure Virtual Box starts with system and disable all other startup applications
\end{itemize*}

@@

java -jar $selenium.jar -interactive

@@

function FindProxyForURL(url, host) {
   if(shExpMatch(url, '*/selenium-server/*')) {
       return 'PROXY localhost:4444; PROXY proxy.ourdomain.dom:8080';
   } else if (shExpMatch(host, '*dev.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*qa.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*staging.ourdomain.dom*')) {
       return 'DIRECT';
   } else {
       return 'PROXY proxy.ourdomain.dom:8080';
   }
}

@@

function FindProxyForURL(url, host) {
   if(shExpMatch(host, '*torsim')) {
       return 'PROXY localhost:8118';
   }
   return 'PROXY localhost:4444; DIRECT';
}

@@

ExitPolicyRejectPrivate 0

@@

\begin{enumerate*}
  \item Generate a private ssh key for the user with the command: \verb+ssh-keygen+, when prompted for a password enter nothing.
  \item SSH to the other host systems on the network, and copy the contents of \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the destination system.
  \item Install ruby so that the management script can be run:
    \begin{verbatim}
sudo apt-get install ruby rubygems
    \end{verbatim}
  \item Ensure the script \verb+run_simulation.rb+ is started on login.
\end{enumerate*}

@@

\begin{enumerate*}
  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
  \begin{verbatim}
deb http://deb.torproject.org/torproject.org lucid main
  \end{verbatim}
  \item Install the GPG key for the Tor packages:
  \begin{verbatim}
gpg --keyserver keys.gnupg.net --recv 886DDD89
gpg --export A3C4F0F979CAA22CDBA8F512EE8CBC9E886DDD89 | sudo apt-key add -
  \end{verbatim}
  \item Install Tor:
  \begin{verbatim}
sudo apt-get update && sudo apt-get install tor
  \end{verbatim}
\end{enumerate*}

@@

\begin{enumerate*}
  \item Deploy the experiment files onto the client system.
  \item Install Ruby
  \item Install the bundler ruby gem with the command:
    \begin{verbatim}
gem install bundler
    \end{verbatim}
  \item Install the required client ruby gems by executing the bundler from the client directory in the deployed experiment files.
    \begin{verbatim}
bundle install
    \end{verbatim}
  \item Ensure that the client script is executed at system startup.
\end{enumerate*}

@@

>>>>

@@

The Apache web server is the most prevalent web server used on the internet
\parencite{2010:dq}.  \cite{:qf}

@@

The experiment involves two stages, an initial configuration stage to prepare
equipment, install software, configure and test the design and the final stage
of executing the simulation to capture packet traces.

@@

Four identical IBM desktop computer systems were prepared and arranged as shown
in figure \ref{physical-setup}.

\begin{figure}[H]
  \centering\includegraphics[scale=0.7]{physical-setup}
  \caption{Physical Setup}
  \label{physical-setup}
\end{figure}

@@

Table \ref{table:hosts} shows the role of each system in the experiment as well
as the edition of operating system in use and the IP address they were
configured with on the network.

\begin{tabular}{lrr}
  \toprule
  Role & Operating System Version & IP Address\\
  \midrule
  Client Host & Desktop & 192.168.0.100\\
  Server Host & Desktop & 192.168.0.001\\
  Tor Host & Desktop & 192.168.0.102\\
  \midrule
  Sniffing System & Server & 192.168.0.200\\
  \midrule
  Client Guest & Desktop & 192.168.0.16\\
  Server Guest & Server & 192.168.0.17\\
  Tor Network Guest & Server & 192.168.0.18\\
  \botomrule
  \label{table:hosts}
\end{tabular}

@@

@@

The sniffing system was based on a basic installation of the Ubuntu 10.04 server
operating system with no additional packages installed.

An init.d script was installed to execute the tcpdump program with a specific
filter string after the system had powered on. All capture files were limited to
1mb in size and put into a time stamped directory. To ensure that only relevant
packets were collected the filter string was tuned for each phase of the
experiment. The filter string for each phase is shown below.

Phase 1:
\begin{lstlisting}[language=sh]
dst port 443
\end{lstlisting}

Phase 2 and 3:
\begin{lstlisting}[language=sh]
dst port 5000-5015
\end{lstlisting}

@@

\begin{itemize*}
  \item Install Ubuntu 10.04 Desktop Operating System
    \begin{itemize*}
      \item Use entire disk
      \item Set time zone to GMT +8 WST (Perth)
    \end{itemize*}
  \item Turn off automatic package updates
  \item Turn off power saving features
  \item Install OpenSSH Server
  \item Add Virtual Box repository to sources.lst
  \item Update sources and install Virtual Box
  \item Ensure Virtual Box starts with system and disable all other start
    up applications
\end{itemize*}

@@

\begin{lstlisting}[language=sh]
java -jar $selenium.jar -interactive
\end{lstlisting}

@@

\begin{lstlisting}[language=sh]
function FindProxyForURL(url, host) {
   if(shExpMatch(url, '*/selenium-server/*')) {
       return 'PROXY localhost:4444; PROXY proxy.ourdomain.dom:8080';
   } else if (shExpMatch(host, '*dev.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*qa.ourdomain.dom*')) {
       return 'DIRECT';
   } else if (shExpMatch(host, '*staging.ourdomain.dom*')) {
       return 'DIRECT';
   } else {
       return 'PROXY proxy.ourdomain.dom:8080';
   }
}
\end{lstlisting}

@@

\begin{lstlisting}[language=sh]
function FindProxyForURL(url, host) {
   if(shExpMatch(host, '*torsim')) {
       return 'PROXY localhost:8118';
   }
   return 'PROXY localhost:4444; DIRECT';
}
\end{lstlisting}

@@

\begin{lstlisting}[language=sh]
ExitPolicyRejectPrivate 0
\end{lstlisting}

@@

\begin{enumerate*}
  \item Generate a private ssh key for the user with the command:
    \verb+ssh-keygen+, when prompted for a password enter nothing.
  \item SSH to the other host systems on the network, and copy the contents of
    \verb+$HOME/.ssh/id_rsa.pub+ into \verb+$HOME/.ssh/authorized_keys+ on the
    destination system.
  \item Install ruby so that the management script can be run:
    \begin{lstlisting}[language=sh]
sudo apt-get install ruby rubygems
    \end{lstlisting}
  \item Ensure the script \verb+run_simulation.rb+ is started on login.
\end{enumerate*}

@@

\begin{enumerate*}
  \item Edit the file \verb+/etc/apt/sources.lst+ and add the line:
    \begin{lstlisting}[language=sh]
deb http://deb.torproject.org/torproject.org lucid main
    \end{lstlisting}
  \item Install the GPG key for the Tor packages:
    \begin{lstlisting}[language=sh]
gpg --keyserver keys.gnupg.net --recv 886DDD89
gpg --export A3C4F0F979CAA22CDBA8F512EE8CBC9E886DDD89 | sudo apt-key add -
    \end{lstlisting}
  \item Install Tor:
    \begin{lstlisting}[language=sh]
sudo apt-get update && sudo apt-get install tor
    \end{lstlisting}
\end{enumerate*}

@@

\begin{enumerate*}
  \item Deploy the experiment files onto the client system.
  \item Install Ruby
  \item Install the bundler ruby gem with the command:
    \begin{lstlisting}[language=sh]
gem install bundler
    \end{lstlisting}
  \item Install the required client ruby gems by executing the bundler from the client directory in the deployed experiment files.
    \begin{lstlisting}[language=sh]
bundle install
    \end{lstlisting}
  \item Ensure that the client script is executed at system startup.
\end{enumerate*}

@@

\subsection{Processing of Results}

The experiment was run over the course of 8 weeks yielding three sets of sample
data.

\begin{tabular}{lrr}
  \toprule
  Phase & Size (bytes) & Number of sessions\\
  \midrule
  HTTPS & 2326328 & 236659\\
  HTTP over Tor & 2869624 & 168876\\
  HTTPS over Tor & 1591112 & 95203\\
  \bottomrule
  \label{table:datasets}
\end{tabular}

The data captured was in the form of 1mb capture files which were recombined
with mergecap and processed by NetAI to produce ARFF format files for use by
Weka. Each data set were given the nominal classification 'http',
'http_over_tor' and 'https_over_tor', all other nominal attributes were removed.

% vim: fdm=syntax tw=80

### 2011-01-03 thesis/thesis.tex
More write up work, redid the physical setup diagram

>>>>

\chapter{Results}

\section{Results}

The classification results are tabulated below. The best performing algorithm
j4.8 was able to classify HTTP over Tor with 97.8\% accuracy and a false
positive rate of 4.3\%. HTTPS was more easily identified with a 97\% accuracy
and low false positive rate of 0.7\%.

\begin{tabular}{lrrr}
  \toprule
  & True Positive Rate & False Positive Rate & ROC \\
  \midrule
  Random Forest\\
  \midrule
  HTTPS & 0.957 & 0.036\\
  HTTP over Tor & 0.937 & 0.037\\
  HTTPS over Tor & 0.977 & 0.003\\
  \midrule
  j4.8 With 10 fold cross validation\\
  \midrule
  HTTPS & 0.951 & 0.04\\
  HTTP over Tor & 0.978 & 0.043\\
  HTTPS over Tor & 0.97 & 0.007\\
  \midrule
  Random Tree\\
  \midrule
  HTTPS & 0.961 & 0.046\\
  HTTP over Tor & 0.906 & 0.04\\
  HTTPS over Tor & 0.955 & 0.01\\
  \midrule
  Adaboost\\
  \midrule
  HTTPS & 0.95 & 0.001\\
  HTTP over Tor & 0.999 & 0.324\\
  HTTPS over Tor & 0 & 0\\
  \botomrule
  \label{table:results}
\end{tabular}

\chapter{Discussion of Results}

\section{Limitations}

The classifiers developed within this experiment have been trained against
a relatively small sample set of simulated data, which may only represent
a small fraction of the width and breadth of conditions available on a wider
area network. The characteristics that allow for classification of Tor network
may be masked by the natural variability introduced by a heterogeneous network.

\section{Addressing Research Questions}

\subsection{Can the traffic be classified using automated matching techniques?}

Yes.

\subsection{Do these networks have characteristics that make them readily
distinguishable using heuristics based matching?}

\subsection{Do they have characteristics that make them distinguishable using a
machine learning technique?}

Yes.

\subsection{How long does a user have to be connected to the network before a
confident match can be made?}

Don't know... yet.

\section{Possible Implications of Results}

\chapter{Conclusion}

While it is difficult to draw a broad conclusion with the limited nature of the
experiment conducted, the findings suggest that the strategies used by anonymous
networks to thwart identity revealing traffic analysis may make them easier to
identify.

Research has shown that the low latency design of Tor means it is vulnerable to
traffic analysis attacks that correlate traffic patterns with users. This
transparency should in fact make Tor more difficult to classify than more
'anonymous' network designs which employ batching and traffic normalizing.
Steganography is a difficult problem and it may be that the extra traffic
required to maintain the Tor network means it will always be easily
differentiated from regular encrypted traffic.
